\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and the Sliding Window Filter

### 2014-12-31 Report/project_report.tex
Added comment about synthetic data noise
Ran out of brain-compute

\subsection{Experiment 3: Effect of feature density}
In order to investigate the effect of feature density on the performance of the MSCKF and SWF, we modified the ``Starry Night'' dataset by creating synthetic feature distributions with larger spatial extents and more features than the original dataset.
We constructed each dataset so that the larger maps contained the same features as the smaller maps, plus additional features to make up the difference.
Although the camera measurements in these datasets are synthetic, the IMU data are unchanged from the original dataset.
Figure \ref{fig:trajectory_groundtruth_100lessnoisy} shows the feature distribution for the 100-feature synthetic dataset.
By generating longer feature tracks and increasing the number of features visible at each time step, these synthetic datasets allowed for a clearer comparison between the MSCKF and SWF.

@@

Although the SWF appears to produce more accurate pose estimates than the MSCKF in many cases, the MSCKF has the advantage of being less computationally intensive than the SWF, and of having better consistency properties.
The MSCKF may be a better choice of algorithm in applications where computational resources are limited, or where a consistent estimate of state uncertainty is desirable.

>>>>

\subsection{Experiment 3: Effect of feature density}
In order to investigate the effect of feature density on the performance of the MSCKF and SWF, we modified the ``Starry Night'' dataset by creating synthetic feature distributions with larger spatial extents and more features than the original dataset.
We constructed each dataset so that the larger maps contained the same features as the smaller maps, plus additional features to make up the difference.
In each dataset, the IMU data remained unchanged from the original dataset and we corrupted the synthetic camera measurements with zero-mean Gaussian noise.
Figure \ref{fig:trajectory_groundtruth_100lessnoisy} shows the feature distribution for the 100-feature synthetic dataset.
By generating longer feature tracks and increasing the number of features visible at each time step, these synthetic datasets allowed for a clearer comparison between the MSCKF and SWF.

@@

Although the SWF appears to produce more accurate pose estimates than the MSCKF in many cases, the MSCKF has the advantage of being less computationally intensive than the SWF, and of having better consistency properties.
The MSCKF may be a better choice of algorithm in applications where computational resources are limited and the operational environment is feature-rich.
